---
title: "GOV 1005 Final Project: Using Yelp to Analyze What Type of Restaurants Make Good Date Spots "
author: "Grace Pan"
date: "4/23/2020"
output: html_document
---

**What makes a restaurant a good date spot? Will my date like barbecue or sushi? This project uses a geographically diverse subset of Yelp data across North America to analyze and predict what type of restaurants make good date spots. The researcher scrapes keywords relating to dating in Yelp user comments as a proxy to determine whether a restaurant is a good date spot. The results are useful not only for individuals trying to impress their dates, but also for professionals in the restaurant business looking to attract more customers.** 


```{r setup, include = FALSE}

fillColor = "#D32323" # yelpy-red
fillColor2 = "#0073BB" # blue

library(tidyverse) #  data manipulation and graphs
library(stringr) #  string manipulation
library(lubridate) #  date manipulation
library('wordcloud') #  wordcloud
library(tidytext) # tidy implementation of NLP methods
library(DT)       # table format display of data
library(leaflet) # maps
library(ggplot2)
library(mapview)
library(fastDummies)
library(janitor)
library(gt)
library(plyr)
library(plotly)

# library(igraph) #  graphs
# library(ggraph) #  graphs
# 
# library(topicmodels) # for LDA topic modelling 
# library(tm) # general text mining functions, making document term matrixes
# library(SnowballC) # for stemming

library(textcat)
```

The following visualizations analyze a subset of Yelp data in seven metropolitan cities: Montreal, QC; Madison, WI; Pittsburgh, PA; Toronto, ON; Cleveland, OH; Las Vegas, NV; and Charlotte, NC.

```{r 1, include = FALSE, cache = TRUE}

# Read in data sets and joined together biz/tip and biz/review.

business <- read_csv("raw-data/yelp_subset.csv") 

business <- business %>%
  select(business_id, name, address, city, state, postal_code , latitude , longitude,  stars ,  is_open, categories) %>%
  filter(is_open == 1)

reviews <- read_csv("raw-data/yelp_review_1000.csv")


reviews <- reviews %>%
  select(business_id, text)

business_reviews_join <- business %>%
  left_join(reviews, by = "business_id") %>%
  filter(! is.na(text), ! is.na(name))
 
```

## 10 Most Popular Categories of Business

```{r 2, echo = FALSE, cache= TRUE}

# PLOTTING THE 10 MOST POPULAR CATEGORIES OF BUSINESS IN A BAR PLOT

# Made a new tibble called categories. I used str_split to separate the descriptors originally divided by semicolons. I renamed the categories column as "Name."

categories = str_split(business$categories,";")
categories = as.data.frame(unlist(categories))
colnames(categories) = c("Name")

# Found the top 10 categories of business by grouping, counting, and arranging in descending order. 

categories_head <- categories %>%
  group_by(Name) %>%
  summarise(Count = n()) %>%
  arrange(desc(Count)) %>%
  ungroup() %>%
  mutate(Name = reorder(Name,Count)) %>%
  head(10) 

# Plotted the top ten categories of business in a bar plot and formatted accordingly. 

categories_head_plot <- categories_head %>%
  ggplot(aes(x = Name,y = Count)) +
  geom_bar(stat='identity', colour="white", fill =fillColor) +
  geom_text(aes(x = Name, y = 1, label = paste0("(",Count,")",sep="")),
            hjust=0, vjust=.5, size = 4, colour = 'black',
            fontface = 'bold') +
  labs(x = 'Name of Category', y = 'Count', 
       title = 'Top 10 Categories of Business',
       subtitle = "Restaurants, Food, and Shopping Business Prove Most Popular",
       caption = "Source: Yelp") +
  coord_flip() + 
  theme_bw()

categories_head_plot
 
```


```{r q2b, include = FALSE, cache= TRUE}

ggsave("categories_head_plot.png")

```


## Map of Business Parties in Las Vegas

```{r 3, echo = FALSE, cache= TRUE}

# MAP OF BUSINESS PARTIES IN LAS VEGAS

# Filtered for all businesses located in Las Vegas. Used median longitude and latitude coordinates in dataset to set the view of the map.

LasvegasCoords = business %>% filter(city == "Las Vegas")

center_lon = median(LasvegasCoords$longitude,na.rm = TRUE)
center_lat = median(LasvegasCoords$latitude,na.rm = TRUE)

# Layered coordinates onto National Geographic World Map. Formatted settings of map.
las_vegas_map <- leaflet(LasvegasCoords) %>% 
  addProviderTiles("Esri.NatGeoWorldMap") %>%
  addCircles(lng = ~longitude, lat = ~latitude)  %>%
  setView(lng=center_lon, lat=center_lat,zoom = 13)

las_vegas_map 


```

```{r q3b, include = FALSE, cache= TRUE}

las_vegas_map <- leaflet() %>% addTiles()
mapshot(las_vegas_map, file = "las_vegas_map.png")

# write_rds LasVegasCoord


```

## Map of Business Parties in Montreal 

```{r 4, echo = FALSE, cache= TRUE}

# MAP OF BUSINESS PARTIES IN MONTREAL

# Filtered for all businesses located in Montreal. Used median longitude and latitude coordinates in dataset to set the view of the map.


MontrealCoords = business %>% filter(city == "Montreal")

center_lon = median(MontrealCoords$longitude,na.rm = TRUE)
center_lat = median(MontrealCoords$latitude,na.rm = TRUE)

# Layered coordinates onto National Geographic World Map. Formatted settings of map.

montreal_map <- leaflet(MontrealCoords) %>% 
  addProviderTiles("Esri.NatGeoWorldMap") %>%
  addCircles(lng = ~longitude, lat = ~latitude)  %>%
  setView(lng=center_lon, lat=center_lat,zoom = 13)

montreal_map 

```

## Detecting Date Spots based on Yelp Review Date Keywords

```{r 5, include= FALSE, cache= TRUE}

# I mutated a new column called detect that detects the strings such as "date," "boyfriend," and "girlfriend."

detect <- business_reviews_join %>%
  filter(grepl('Restaurant|Food|Bars', categories)) %>%
  mutate(string_detect = str_detect(text, paste(c("date", "boyfriend", "girlfriend", "husband", "wife", "anniversary", "Valentine", "romantic", "cozy"), collapse = "|")))

# Calculating percentage of date spots

detect_percent <- detect %>%
  filter(string_detect == TRUE) %>%
  count() / 6760

detect_percent

```

Out of the restaurants in the dataset, **`r detect_percent`** percent are considered good date spots, based on a date-related keyword search of Yelp user reviews. 

```{r 6, include = FALSE, cache= TRUE}

parentheses = paste(c("\\(New\\)", "\\(Tradit", "\\(Traditional\\)", "ional\\)"), collapse = "|")

x <- business_reviews_join %>%
  select(business_id, categories) %>%
  filter(grepl('Restaurant|Food|Bars', categories)) %>%
  mutate(categories = str_replace_all(categories, parentheses, "")) %>%
  separate(categories,sep=";",fill="right",into=c("A","B","C","D", "E", "F", "G", "H","I", "J", "K", "L", "M", "N", "O", "P")) %>%
  pivot_longer(-business_id, names_to = "Group",values_to="Food") %>%
  dummy_cols(select_columns = "Food") %>%
  filter(is.na(Food)==FALSE) %>%
  select(c("business_id", "Food_American ", "Food_Asian Fusion"  , "Food_Bagels"  ,  "Food_Bakeries"  , "Food_Barbeque", , "Food_Bars", "Food_Breakfast & Brunch", "Food_British", "Food_Bubble Tea"  ,  "Food_Buffets"  ,"Food_Burgers" , "Food_Cafes",  "Food_Cajun/Creole" , "Food_Canadian "   , "Food_Caribbean"  ,  "Food_Cheesesteaks"  , "Food_Chicken Shop" ,"Food_Chocolatiers & Shops", "Food_Chinese"  ,"Food_Comfort Food" ,  "Food_Creperies",  "Food_Delicatessen",  "Food_Delis" ,  "Food_Diners" , "Food_Desserts"  , "Food_Dive Bars", "Food_Donuts" ,  "Food_Ethiopian" , "Food_Ethnic Food" , "Food_Fast Food"  , "Food_Filipino" , "Food_Fish & Chips"  ,   "Food_Food Court", "Food_French" ,  "Food_Gastropubs" , "Food_Greek"  ,"Food_Gluten-Free"   ,  "Food_Halal" , "Food_Hawaiian"  ,"Food_Hot Dogs"   , "Food_Ice Cream & Frozen Yogurt"  , "Food_Indian"  ,"Food_Irish" , "Food_Japanese" ,  "Food_Italian"   , "Food_Juice Bars & Smoothies", "Food_Korean" ,"Food_Lebanese", "Food_Live/Raw Food"  , "Food_Local Flavor"  ,  "Food_Mediterranean" , "Food_Malaysian"  ,   "Food_Mexican" , "Food_Middle Eastern" , "Food_New Mexican Cuisine"  ,  "Food_Noodles"    , "Food_Pakistani", "Food_Pizza"  , "Food_Portuguese",  "Food_Popcorn Shops" ,  "Food_Poutineries"  , "Food_Ramen" ,    "Food_Sandwiches", "Food_Salad", "Food_Seafood",  "Food_Smokehouse", "Food_Southern", "Food_Soup" , "Food_Soul Food", "Food_Specialty Food" , "Food_Steakhouses"  , "Food_Tapas/Small Plates", "Food_Tex-Mex", "Food_Tiki Bars" ,  "Food_Thai" , "Food_Vegetarian",  "Food_Vegan",  "Food_Vietnamese"  , "Food_Waffles", "Food_Wraps")) %>%
  clean_names() %>%
  group_by(business_id) %>%
  summarise_all(funs(sum))


# Create row with sum of restaurant type counts

x_sum <- rbind(x, c("total", colSums(x[,2:81])))


# Select only the row which has the sums 

summed <- x_sum %>%
  slice (322)
 
# Reshape data and subset to columns with at least 10 count

saveColumns <- summed %>%
  pivot_longer(-business_id, names_to="type", values_to="count")

saveColumns$count <- as.numeric(saveColumns$count)

saveColumns <- saveColumns %>%
  filter(count >= 10)


# Select columns from original table using the column labels from SaveColumns which have at least than 10 count

x_sum <- x_sum %>%
  select(business_id, contains(saveColumns$type))

# Consolidate food types into cuisines

# x_consolidate <- x_sum %>% 
#   mutate(cuisine_asian= case_when( food_asian_fusion >= 1 | food_chinese >= 1 ~ 1,
#                                    TRUE ~ 0)) 
    

```

```{r r6, include = FALSE, cache= TRUE}

# Merge restaurant type and string detect datasets

merged <- x_sum %>%
  full_join(detect, by = "business_id") 

# Mutate all values > 1 to 1 (in order to correct the lm process)

       
           
merged$food_american <- revalue(merged$food_american, c("2" = "1", "3" = "1")) 
merged$food_asian_fusion <- revalue(merged$food_asian_fusion, c("2" = "1", "3" = "1")) 
merged$food_bakeries <- revalue(merged$food_bakeries, c("2" = "1", "3" = "1")) 
merged$food_chinese <- revalue(merged$food_chinese, c("2" = "1", "3" = "1")) 
merged$food_japanese <- revalue(merged$food_japanese, c("2" = "1", "3" = "1")) 
merged$food_bars <- revalue(merged$food_bars, c("2" = "1", "3" = "1")) 
merged$food_breakfast_brunch <- revalue(merged$food_breakfast_brunch, c("2" = "1", "3" = "1")) 
  
  
# one <- function () {
#   result <- revalue( c("2" = "1"))
# }
#     
# merged %>% 
#   select_if(is.character) %>%
#   mutate_all( ~ one())

```

## Regression Model for Effect of Type of Restaurant on Restaurant Ratings

```{r 7, echo = FALSE, cache= TRUE}

# Regression gt for effect of type of restaurant on restaurant ratings

merged_lm_stars <- merged %>%
  select(- c(business_id, name, address, city, state, postal_code, latitude, longitude, is_open, categories, text, string_detect)) %>%
  slice (-330) 


# lm_stars <- lm(stars~
# food_american + food_asian_fusion + food_bakeries  + food_bars + food_breakfast_brunch + food_burgers + food_cafes + food_canadian  + food_chinese + food_desserts + food_fast_food + food_japanese + food_italian  + food_mexican + food_pizza + food_sandwiches + food_seafood + food_specialty_food + food_steakhouses, data = merged)

lm_stars <- lm(stars ~ ., data = merged_lm_stars)

lm_stars_tidy <- lm_stars %>%
  tidy(conf.int = TRUE) %>%
  select(term, estimate, conf.low, conf.high) %>%
  arrange(desc(estimate)) 

lm_stars_gt <- lm_stars_tidy %>%
  gt() %>%
  fmt_number(columns = vars(estimate, conf.low), decimals = 3) %>%
  fmt_number(columns = vars(conf.high), decimals = 4) %>%
  tab_header(
    title = "Effect of Type of Restaurant on Restaurant Ratings",
    subtitle = "Data from Yelp") %>%
    cols_label(
      "term" = "Variable",
      "estimate" = "Estimate",
      "conf.low" = "Lower bound",
      "conf.high" = "Upper bound") 

lm_stars_gt

```

## Regression Model for Effect of Type of Restaurant on Likelihood of Being a Date Spot

```{r r 8, echo = FALSE, cache= TRUE}

# Regression gt for effect of type of restaurant on likelihood of being a date spot (based on string detect)


merged_lm_date <- merged %>%
  select(- c(business_id, name, address, city, state, postal_code, latitude, longitude, is_open, categories, text, stars)) %>%
  slice (-330) 

lm_date <- lm(string_detect ~ . , data = merged_lm_date)


lm_date_tidy <- lm_date %>%
  tidy(conf.int = TRUE) %>%
  select(term, estimate, conf.low, conf.high) %>%
  arrange(desc(estimate))


lm_date_gt <- lm_date_tidy %>%
  gt() %>%
  fmt_number(columns = vars(estimate, conf.low), decimals = 3) %>%
  fmt_number(columns = vars(conf.high), decimals = 4) %>%
  tab_header(
    title = "Effect of Type of Restaurant on Likelihood of Being a Date Spot",
    subtitle = "Data from Yelp") %>%
    cols_label(
      "term" = "Variable",
      "estimate" = "Estimate",
      "conf.low" = "Lower bound",
      "conf.high" = "Upper bound")

lm_date_gt

```

```{r 9, echo = FALSE, cache= TRUE}

# Creating plot for Rating Regression based on Type of Food. 
# Dropped intercept
# Hover label over food type
# Allow user to select 3 inputs, 


lm_stars_plot <- lm_stars_tidy %>% 
  slice(-1) %>%
  ggplot(aes(x = reorder(term, -estimate), y = estimate, group = 1, 
             text = paste("Cuisine: ", term,
                          "<br>Coefficient: ", estimate
                                                   ))) +
  geom_bar(stat = "identity", fill = "light blue", ) +
  labs(title = "Effect of Restaurant Type on User Ratings", subtitle = "Ratings on a 1-5 scale",
       x = "Type of Food", y = "Coefficient",caption = "Source: Yelp") +
  theme_classic() +
  theme(axis.text.x= element_blank(),
        axis.ticks.x=element_blank())

lm_stars_plot

ggplotly(lm_stars_plot, tooltip = "text") %>%
   layout(title = list(text = paste0('Effect of Restaurant Type on User Ratings',
                                    '<br>',
                                    '<sup>',
                                    'Ratings on a 1-5 scale',
                                    '</sup>')),
    annotations = 
          list(x = 1, y = -.08, text = "Source: Yelp", 
                showarrow = F, xref='paper', yref='paper', 
                xanchor='right', yanchor='auto', xshift=0, yshift=0,
                font=list(size=12)))



# plot_ly(data = lm_stars_tidy,
#         x = ~term,
#         y = ~estimate,
#         hoverinfo = 'text'
#         )



lm_date_plot <- lm_date_tidy %>% 
  slice(-1) %>%
  ggplot(aes(x = reorder(term, -estimate), y = estimate, group = 1, 
             text = paste("Cuisine: ", term,
                          "<br>Coefficient: ", estimate
                                                   ))) +
  geom_bar(stat = "identity", fill = "dark green", ) +
  labs(title = "Effect of Restaurant Type on Date Appropriateness", subtitle = "Date appropriateness determined by scraping user reviews for date-related keywords",
       x = "Type of Food", y = "Coefficient",caption = "Source: Yelp") +
  theme_classic() +
  theme(axis.text.x= element_blank(),
        axis.ticks.x=element_blank())

lm_date_plot

ggplotly(lm_date_plot, tooltip = "text") %>%
  layout(title = list(text = paste0('Effect of Restaurant Type on Date Appropriateness',
                                    '<br>',
                                    '<sup>',
                                    'Date appropriateness determined by scraping user reviews for date-related keywords',
                                    '</sup>')),
          annotations = 
          list(x = 1, y = -.08, text = "Source: Yelp", 
                showarrow = F, xref='paper', yref='paper', 
                xanchor='right', yanchor='auto', xshift=0, yshift=0,
                font=list(size=12)))




```

